\documentclass[../main.tex]{subfiles}

\newcommand{\tema}{\textbf{SENSITIVITY ANALYSIS}}
\begin{document}
\printanswers
\input{header.tex}
% ============================
% ADDITION OF A NEW CONSTRAINT
% ============================
\begin{questions}
\question % Gupta EXERCISES 6.6-41

Consider the following table which represents an optimal solution to some L.P.P.:

{\centering
  \begin{tabular}{crrrrrrrrrr}
    \toprule
    &$c_j$&2&4&1&3&2&0&0&0&\\
    \midrule
    $c_B$&Basis&$x_1$&$x_2$&$x_3$&$x_4$&$x_5$&$x_6$&$x_7$ &$x_8$& b\\
    \midrule
    2&$x_1$&1&0&0&$-1$&0&\nicefrac{1}{2}&\nicefrac{1}{5}&$-1$&3\\
    4&$x_2$&0&1&0&2&1&$-1$&0&\nicefrac{1}{2}&1\\
    1&$x_3$&0&0&1&$-1$&$-2$&5&$\nicefrac{-3}{10}$&2&7\\
    \midrule
    %$Z_j = \sum c_Ba_{ij}$& &7&2&5&1&2&0&\\
    &$\overline{c_j} = c_j - Z_j$ &0&0&0&$-2$&0&$-2$&$\nicefrac{-1}{10}$&$-2$&17\\
    \bottomrule
  \end{tabular}
  \par}

If the additional constraint $2x_1 + 3x_2 - x_3 + 2x_4 + 4 x_5 \leq 5$ is annexed to the system, will there be any change in the optimal solution? Justify your answer.


\begin{solution}{}
  Sustituyendo los valores de $x_1, x_2, x_3$ en la restricci贸n que se desea agregar se tiene que \[ 2(3) + 3(1) - 7+ 0 + 0 = 6 + 3 - 7 + 0 +0 = 2 \]

  Los valores de la soluci贸n 贸ptima satisfacen la nueva restricci贸n ($2 \leq 5$) por lo tanto no hay cambio en el sistema
\end{solution}
\vspace{5mm}

\question % Gupta EXERCISES 6.6-43
A firm produces three items A, B, and C and requires two types of resources --man hours and raw matrial. The following L.P. problem has been formulated to determine the optimum production schedule that maximizes the total profit:

\[ \max Z = 3y_1 + y_2 + 5y_3\]

{\centering
  subject to
  \vspace{2mm}

  \sysdelim..%
  \sysalign{r,r}%
  \systeme[y_1y_2y_3]%
  {%
    6y_1 + 3y_2 + 5y_3 \leq 45@ (man-hours),
    3y_1 + 4y_2 + 5y_3 \leq 30@ (\text{raw material})
  }
  \vspace{2mm}

  $y_1, y_2, y_3 \geq 0$
  \par}

\vspace{3mm}

where $y_1, y_2, y_3$ are the number of items A, B, and C. Find the optimal solution.
\vspace{3mm}

\begin{parts}
  \part Find the range on the unit profit of product A. If $c_1 = 4$, what is the optimal solution?
  \part If additional 10 units of raw material can be obtained at a cost of \$ 12, is it profitable to do so?
  \part If the available raw material is increased to 50 units, what is the optimal solution?
  \part Due to ``technological breakthrough'' the raw material required by part B is reduced to 2 units. Will affect the optimal solution?
  \part If a supervision constraint, $2y_1 + y_2 + 3y_3 \leq 20$ is added to the original problem, how is the optimal solution affected?
\end{parts}
\end{questions}
\end{document}